Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels

### 2018-05-11 articles/formalism/sections/real_space_formalism.tex
Fixed up 3.4

\paragraph{Convolution kernel.} We can also formulate the real space operator as a convolution operation, where the scalar field at $\hat n_e$ gathers contributions from the Stokes fields.  This is based around the inverse rotation (to align the coordinate system at $\hat{n}_e$ with that at $\hat{n}_q$).  The inverse rotation Euler angles relates to the forward rotation Euler angles by the following relations: $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$. Since the kernel only depends on the cosine of the Euler angle $\beta$, it is immune to changes in its sign. The operator equation can be expressed as a function of the Euler angle $\gamma_{eq}$ as follows, 
%
\beq \label{eq:qu2eb_convolution_explicit}
\bmat E_e \\ B_e  \emat =- \sum_{q=1}^{N_{\rm pix}}{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \gamma_{eq}) & -\sin(2\gamma_{eq})\\  \sin(2 \gamma_{eq})  & \cos(2 \gamma_{eq}) \emat  \bmat Q_q \\ U_q  \emat \Delta \Omega\,,
\eeq
%
%where $\Delta \Omega$ denotes the pixel area and all the symbols have their usual meaning. 
\revisit{This version of the real space operator would have naturally emerged had we simplified the the equivalent function $\sum_{\ell m} {}_{0}Y^*_{\ell m}(\hat{n}_e){}_{+2}Y_{\ell m}(\hat{n}_q)$ in \eq{eq:qu2eb_gen_kernel}.} This formulation of the real space operator can be interpreted as integrating at some fixed location $\hat{n}_e$ the $E/B$ mode contribution arising from the Stokes parameters at all location $\hat{n}_q$ on the sphere. This operation can be expressed more concisely as follows,
%
\begin{subequations} \label{q:qu2eb_convolution_concise}
\beqry 
[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{eq}) \right) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)}, \label{eq:qu2eb_physical}\\
&=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \star {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
&=& \Bigg\lbrace \mathcal{M}_{B} \star {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \label{eq:qu2eb_convolution} 
\eeqry
\end{subequations}
%
where $\star$ denotes a convolution and $\mathcal{M}_{B}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$. 
%--------------------------------------------------------

%--------------------------------------------------------
\subsection{Evaluating Stokes parameters $Q$ \& $U$ from scalar fields $E$ \& $B$}\label{sec:eb2qu}
The real space operator which translates $E$ \& $B$ fields to Stokes parameters $Q$ \& $U$ can be derived using a similar procedure. Expressed in the matrix-vector notation, inverse operator is given by,
%
\begin{subequations}
\beqry
\bar{P} &=& \bar{T}^{-1} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} *{{}_2\mathcal{Y}} *\tilde T *{{}_0\mathcal{Y}^{\dagger}}\bar{S} \,,  \\
&=&  \bar O^{-1} *\bar{S}\,.
\eeqry
\end{subequations}
%
%The inverse operator $\bar{O}^{-1}$ can be derived by realizing that $\mm^{-1}$ is given by the following expression,
%%
%\beq
%\mm^{-1} = \sum_{\ell m}  {{}_{2}}Y_{\ell m}(\hat n_q) {}_{0}Y^*_{\ell m}(\hat n_e) \, 
%\eeq
%%
The inverse operator expressed in terms of the function $\mm$ given in \eq{eq:qu2eb_gen_kernel} is given by the following equation,
%
\beq
{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & -\sin(2\alpha_{qe})\\  \sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,,
\eeq
%
where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}. Note that the kernel in the above equation differs from the one in \eq{eq:op_qu2eb_rad} by a change in sign on the off-diagonals of the block matrix. When expressed in terms of the same set of Euler angles used to define the operator $\bar{O}$, it can be shown that the different forms of the real space operator are given by,
%
\beqry
{}_{+2}X(\hat{n}_q) &=& \Bigg\lbrace \mathcal{M}^*_{G} \circ [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm} \textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}\\
{}_{+2}X(\hat{n}_q) &=&  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e}) \cdot  \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm} \textrm{\emph{Radiation kernel}}\,,
\eeqry
%
where all the symbols have the same meaning as defined in \sec{sec:qu2eb}. Note that the conjugated forms of the Green's function and the effective beam for the operator $\bar{O}$ have their roles reversed for the inverse operator $\bar{O}^{-1}$.
%--------------------------------------------------------

@@

\subsection{Decomposing Stokes parameters $Q$ \& $U$  into those corresponding to $E$ \& $B$ modes respectively}
We can only measure the total Stokes vector which is a sum of the Stokes vectors corresponding to the respective scalar modes. The $E$ \& $B$ modes are orthogonal to each other, in the sense that their respective operators are orthogonal to each other as seen in \eq{eq:op_eb_ortho}. It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to $E$ modes and another \vp{\rm B} that purely contribute to the $B$ modes of polarization. In this section we derive the real space operators which operate on the total Stokes vector and yield this decomposition, without ever having to explicitly evaluate the scalar modes. Though the algebra is a little more involved, the derivation is similar to that discussed in \sec{sec:qu2eb}, hence we refrain from presenting the detailed calculations here, but outline the key points. We use the harmonic space projection operators $\tilde O_{E/B}$, defined in \eq{eq:har_eb_op}, to derive the respective real space operators. The Stokes parameters corresponding to each scalar mode are given by the following expressions,

@@

\bar{P}_E &=&  [\bar T^{-1} * {{}_2\mathcal{Y}} *\tilde T * \tilde O_E* \tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}} *\bar T] *\bar{P}  \,, \\
&=& [\frac{1}{4} \bar T^{\dagger } * {{}_2\mathcal{Y}} *\tilde T * \tilde O_E* \tilde T^{\dagger} * {{}_2\mathcal{Y}^{\dagger}} *\bar T ]*\bar{P}  \,, \nonumber \\
&=&  \bar O_{E}*\bar{P} \,,\nonumber \\
\bar{P}_B &=&  [\bar T^{-1}* {{}_2\mathcal{Y}}* \tilde T* \tilde O_B* \tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}}* \bar T]*\bar{P}  \,, \\
&=& [\frac{1}{4} \bar T^{\dagger } * {{}_2\mathcal{Y}} *\tilde T * \tilde O_B* \tilde T^{\dagger} *{{}_2\mathcal{Y}^{\dagger}} *\bar T] *\bar{P}   \,, \nonumber\\
&=&  \bar O_{B}*\bar{P} \,. \nonumber

@@

where the functions ${{}_{ \pm 2}f}_{\ell}(\beta)$ are expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,

@@

\bmat Q_e \\ U_e  \emat_{E/B} &=& \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {{}_{\mi}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} + 2\gamma_{qe}) & \sin(2\alpha_{qe} +2 \gamma_{qe}) \\  -\sin(2\alpha_{qe} +2 \gamma_{qe})  & \cos(2 \alpha_{qe} + 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat  \\ &\pm& {}_{\md}f(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} - 2\gamma_{qe}) &  \sin(2\alpha_{qe} - 2 \gamma_{qe}) \\  \sin(2\alpha_{qe} - 2 \gamma_{qe})  & - \cos(2 \alpha_{qe} - 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat \Bigg\rbrace 0.5 \Delta\Omega  \,, \nonumber 

@@

{}_{+2}X_{E/B}(\hat{n}_e) &=&0.5 \Delta \Omega\sum_{q=1}^{N_{\rm pix}}  {{}_{\mi}f}(\beta_{qe}) e^{-i2 (\alpha_{qe} + \gamma_{qe})} {}_{+2}X(\hat{n}_q) \pm {{}_{\md}f}(\beta_{qe}) e^{i2 (\alpha_{qe} - \gamma_{qe})} {}_{+2}X(\hat{n}_q)^* \,, \nonumber \\
&=& 0.5 \Bigg\lbrace  {}_{+2}X \cdot \mathcal{I}^*_G \pm {}_{+2}X^* \cdot \mathcal{D}_G \Bigg\rbrace \hspace{.5cm }\textrm{\emph{   Radiation kernel}} \,, \\
&=& 0.5 \Bigg\lbrace \mathcal{I}_B \circ {}_{+2}X\pm \mathcal{D}_B \circ {}_{+2}X^* \Bigg\rbrace   \hspace{.5cm } \textrm{\emph {  Convolution kernel}} \,, \label{eq:qu2equbqu_convolution}

@@

where all the symbols have their usual meaning and the explicit multipole dependence of the real space operators has been suppressed for brevity. Note that when the operators $\mathcal{I}^*$ \& $\mathcal{D}$ are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them as $\mathcal{I}^*_G$ \& $\mathcal{D}_G$. When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as a some convolving beam and we denote them as $\mathcal{I}_B$ \& $\mathcal{D}_B$. Note that unlike in the case of the operators $\mm_G$ \& $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ \& $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}^*_{G}$ \& $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.

The operator $\mathcal{I}$ is Hermitian and is a band limited version of the delta function owing to the identity $\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$. For all practical purposes $\mathcal{I}$ acts like an identity operator as is confirmed by the following set of identities: (i) $\mathcal{I}*\mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D}*\mathcal{I}=\mathcal{D}$. $\mathcal{D}$ is a complex but symmetric matrix and $\mathcal{D}^*$ is its inverse in this band limited sense: $\mathcal{D}^**\mathcal{D}=\mathcal{I}$. Using these properties of the operators $\mathcal{I}$ and $\mathcal{D}$, one can verify that the real space operators satisfy the following identities,
%
\begin{subequations}
\beqry
\bar O_E * \bar O_E &=& \bar O_E ~~;~~ \bar O_B * \bar O_B = \bar O_B \,, \\
\bar O_E*\bar O_B &=& 0 \,,\\
\bar O_E + \bar O_B &=& \mathcal{I} \,,
\eeqry
\end{subequations}
%
which are the real space analogues of \eq{eq:har_op_prop}. \footnote{While testing the above stated identities one encounters terms like $\mathcal{D}*\mathcal{I}^*,\mathcal{I}^**\mathcal{I} \textrm{ and }  \mathcal{I}*\mathcal{I}^*$ which cannot be simply interpreted but they always occur in pairs with opposite signs that exactly cancel each other.}

>>>>

\paragraph{Convolution kernel.} We can also formulate the real space operator as a convolution operation, where the scalar field at $\hat n_e$ gathers contributions from the Stokes fields.  This is based around the inverse rotation from the previous section (to align the coordinate system at $\hat{n}_e$ with that at $\hat{n}_q$).  The inverse rotation Euler angles relates to the forward rotation Euler angles by the following relations: $\alpha_{eq}=-\gamma_{qe}$, $\beta_{eq} = -\beta_{qe}$ and  $\gamma_{eq} =-\alpha_{qe}$. Since the kernel only depends on the cosine of the Euler angle $\beta$, it is immune to changes in its sign. The operator equation can be expressed as a function of the Euler angle $\gamma_{eq}$ as follows, 
%
\beq \label{eq:qu2eb_convolution_explicit}
\bmat E_e \\ B_e  \emat =- \sum_{q=1}^{N_{\rm pix}}{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \gamma_{eq}) & -\sin(2\gamma_{eq})\\  \sin(2 \gamma_{eq})  & \cos(2 \gamma_{eq}) \emat  \bmat Q_q \\ U_q  \emat \Delta \Omega\,,
\eeq
%
%where $\Delta \Omega$ denotes the pixel area and all the symbols have their usual meaning. 
\revisit{This version of the real space operator would have naturally emerged had we simplified the the equivalent function $\sum_{\ell m} {}_{0}Y^*_{\ell m}(\hat{n}_e){}_{+2}Y_{\ell m}(\hat{n}_q)$ in \eq{eq:qu2eb_gen_kernel}.} This formulation of the real space operator can be interpreted as integrating at some fixed location $\hat{n}_e$ the $E/B$ mode contribution arising from the Stokes parameters at all location $\hat{n}_q$ on the sphere. This operation can be expressed more concisely as follows,
%
\begin{subequations} \label{q:qu2eb_convolution_concise}
\beqry 
[E + iB](\hat{n}_e) &=& - \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left(\sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} \sqrt{\frac{(\ell-2)!}{(\ell+2)!}} P_{\ell}^{2}(\beta_{eq}) \right) {\Bigg( e^{i2 \gamma_{eq}}   {}_{+2}X (\hat{n}_q) \Bigg)}, \label{eq:qu2eb_physical}\\
&=& \Bigg\lbrace \left[ - \Delta \Omega \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \sqrt{\frac{2 \ell+1}{4 \pi}}Y_{\ell 2}(\beta_{eq},\gamma_{eq}) \right]  \star {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \\
&=& \Bigg\lbrace \mathcal{M}_{B} \star {}_{+2}X \Bigg\rbrace(\hat{n}_e) \,, \label{eq:qu2eb_convolution} 
\eeqry
\end{subequations}
%
where $\star$ denotes a convolution and $\mathcal{M}_{B}$ is merely the conjugated function $\mm^*$ when expressed as a function of the Euler angle $\gamma_{eq}$ it can be thought of as an effective instrument beam pointing to the direction $\hat{n}_e$. 
%--------------------------------------------------------

%--------------------------------------------------------
\subsection{Evaluating Stokes $Q$/$U$ from scalar $E$/$B$}\label{sec:eb2qu}
The real space operator which translates $E$ \& $B$ fields to Stokes parameters $Q$ \& $U$ can be derived using a similar procedure. Expressed in the matrix-vector notation, inverse operator is given by,
%
\begin{subequations}
\beqry
\bar{P} &=& \bar{T}^{-1} {{}_2\mathcal{Y}}\, \tilde T {{}_0\mathcal{Y}^{\dagger}}\bar{S} = \frac{1}{2} \bar{T}^{\dagger} {{}_2\mathcal{Y}} \,\tilde T {{}_0\mathcal{Y}^{\dagger}}\bar{S}\,,  \\
&=&  \bar O^{-1} \bar{S}\,.
\eeqry
\end{subequations}
%
%The inverse operator $\bar{O}^{-1}$ can be derived by realizing that $\mm^{-1}$ is given by the following expression,
%%
%\beq
%\mm^{-1} = \sum_{\ell m}  {{}_{2}}Y_{\ell m}(\hat n_q) {}_{0}Y^*_{\ell m}(\hat n_e) \, 
%\eeq
%%
The inverse operator expressed in terms of the function $\mm$ given in \eq{eq:qu2eb_gen_kernel} is given by the following equation,
%
\beq
{\bar O}^{-1}=-\bmat \mathcal{M}_{r} & -\mathcal{M}_{i} \\  \mathcal{M}_{i}  & \mathcal{M}_{r} \emat_{2 N_{\rm pix} \times 2 N_{pix}} =-{{}_{\mm}f}(\beta_{eq},\ell_{\rm min},\ell_{\rm max})\bmat \cos(2 \alpha_{qe}) & -\sin(2\alpha_{qe})\\  \sin(2 \alpha_{qe})  & \cos(2 \alpha_{qe}) \emat \,,
\eeq
%
where all the symbols have the same meaning as discussed in \sec{sec:qu2eb}. Note that the kernel in the above equation differs from the one in \eq{eq:op_qu2eb_rad} by a change in sign on the off-diagonals of the block matrix. When expressed in terms of the same set of Euler angles used to define the operator $\bar{O}$, it can be shown that the different forms of the real space operator are given by,
%
\beqry
    {}_{+2}X(\hat{n}_q) &=  \sum_{e=1}^{N_{\rm pix}} [E+iB](\hat{n}_{e})\   \mathcal{M}^*_{B}[\hat{n}_e] \hspace{0.8cm} &\textrm{\emph{Radiation kernel}}\,\\
    {}_{+2}X(\hat{n}_q) &= \Bigg\lbrace \mathcal{M}^*_{G} \star [E+iB] \Bigg\rbrace(\hat{n}_q) \hspace{0.8cm} &\textrm{\emph {Convolution kernel}}\,, \label{eq:eb2qu_convolution}
\eeqry
%
where all the symbols have the same meaning as defined in \sec{sec:qu2eb}. Note that the conjugated forms of the Green's function and the effective beam for the operator $\bar{O}$ have their roles reversed for the inverse operator $\bar{O}^{-1}$.
%--------------------------------------------------------

@@

\subsection{Purifying Stokes parameters $Q$/$U$ from $E$/$B$ modes}
We can only measure the total Stokes vector, a sum of the part corresponding to scalar $E$ and the part corresponding to $B$.  The $E$/$B$ modes are orthogonal to each other in the sense that their respective operators are orthogonal to each other as seen in \eq{eq:op_eb_ortho}. It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to $E$ modes and another \vp{\rm B} that purely contribute to the $B$ modes of polarization. In this section we derive the real space operators which operate on the total Stokes vector and yield this decomposition, without ever having to explicitly evaluate the scalar modes. The algebra is more involved, but the derivation is similar to that discussed in \sec{sec:qu2eb}, so we refrain from presenting the detailed calculations here, and outline only the key points. We use the harmonic space projection operators $\tilde O_{E/B}$, defined in \eq{eq:har_eb_op}, to derive the respective real space operators. The Stokes parameters corresponding to each scalar mode are given by the following expressions,

@@

\bar{P}_E &=&  [\bar T^{-1}  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_E \tilde T^{-1}* {{}_2\mathcal{Y}^{\dagger}}\, \bar T] \bar{P}  \,, \\
&=& [\frac{1}{4} \bar T^{\dagger }  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_E  \tilde T^{\dagger}  {{}_2\mathcal{Y}^{\dagger}}\, \bar T ]\bar{P}  \,, \nonumber \\
&=&  \bar O_{E} \bar{P} \,,\nonumber \\
\bar{P}_B &=&  [\bar T^{-1}  {{}_2\mathcal{Y}} \, \tilde T  \tilde O_B \tilde T^{-1} {{}_2\mathcal{Y}^{\dagger}} \bar T]\bar{P}  \,, \\
&=& [\frac{1}{4} \bar T^{\dagger }  {{}_2\mathcal{Y}}\, \tilde T  \tilde O_B \tilde T^{\dagger} {{}_2\mathcal{Y}^{\dagger}}\, \bar T] \bar{P}   \,, \nonumber\\
&=&  \bar O_{B} \bar{P} \,. \nonumber

@@

where the functions ${{}_{ \pm 2}f}_{\ell}(\beta)$ \revisit{Is the prescript correct?} are expressed in terms of $P_{\ell}^2$ Legendre polynomials and are given by the following explicit mathematical forms,

@@

\bmat Q_e \\ U_e  \emat_{E/B} &=& \sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace {{}_{\mi}f}(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} + 2\gamma_{qe}) & \sin(2\alpha_{qe} +2 \gamma_{qe}) \\  -\sin(2\alpha_{qe} +2 \gamma_{qe})  & \cos(2 \alpha_{qe} + 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat  \\ &\pm& {}_{\md}f(\beta_{qe},\ell_{\rm min},\ell_{\rm max}) \bmat \cos(2 \alpha_{qe} - 2\gamma_{qe}) &  \sin(2\alpha_{qe} - 2 \gamma_{qe}) \\  \sin(2\alpha_{qe} - 2 \gamma_{qe})  & - \cos(2 \alpha_{qe} - 2 \gamma_{qe}) \emat  \bmat Q_q \\ U_q  \emat \Bigg\rbrace  \frac{\Delta\Omega}{2}  \,, \nonumber 

@@

{}_{+2}X_{E/B}(\hat{n}_e) &=& 0.5 \Delta \Omega\sum_{q=1}^{N_{\rm pix}}  {{}_{\mi}f}(\beta_{qe}) e^{-i2 (\alpha_{qe} + \gamma_{qe})} {}_{+2}X(\hat{n}_q)  \pm {{}_{\md}f}(\beta_{qe}) e^{i2 (\alpha_{qe} - \gamma_{qe})} {}_{+2}X(\hat{n}_q)^* \,, \nonumber \\
&=& 0.5 \Bigg\lbrace  {}_{+2}X  \, \mathcal{I}^*_G \pm {}_{+2}X^* \, \mathcal{D}_G \Bigg\rbrace \hspace{.5cm } \textrm{\emph{   Radiation kernel}} \,, \\
&=& 0.5 \Bigg\lbrace \mathcal{I}_B \star {}_{+2}X\pm \mathcal{D}_B \star {}_{+2}X^* \Bigg\rbrace   \hspace{.5cm } \textrm{\emph {  Convolution kernel}} \,, \label{eq:qu2equbqu_convolution}

@@

where all the symbols have their usual meaning and the explicit multipole dependence of the real space operators has been suppressed for brevity. Note that when the operators $\mathcal{I}^*$ and $\mathcal{D}$ are expressed in terms of the Euler angles $(\alpha_{qe},\beta_{qe},\gamma_{qe})$ they can be interpreted as the Greens functions and  we denote them as $\mathcal{I}^*_G$ and $\mathcal{D}_G$. When expressed as function of Euler angles $(\alpha_{eq},\beta_{eq},\gamma_{eq})$ corresponding to the inverse rotations they can be interpreted as a some convolving beam and we denote them as $\mathcal{I}_B$ and $\mathcal{D}_B$. Note that unlike in the case of the operators $\mm_G$ and $\mm_B$ which have different shapes owing to their dependence on Euler angles $\alpha$ and $\gamma$ respectively, the operators $D_G$ and $D_B$ are identical since $(\alpha_{qe}-\gamma_{qe}) = (\alpha_{eq}-\gamma_{eq})$, while $\mathcal{I}^*_{G}$ and $\mathcal{I}_B$ are related by conjugation since  $(\alpha_{qe}+\gamma_{qe}) = -(\alpha_{eq}+\gamma_{eq})$.

The operator $\mathcal{I}$ is Hermitian and is a band limited version of the delta function owing to the identity $\lim_{\ell \rightarrow \infty} \mathcal{I} = \delta(\hat{n}_i - \hat{n}_j)$. For all practical purposes $\mathcal{I}$ acts like an identity operator as is confirmed by the following set of identities: (i) $\mathcal{I} \mathcal{I}=\mathcal{I}$ ; (ii) $\mathcal{D} \mathcal{I}=\mathcal{D}$. $\mathcal{D}$ is a complex but symmetric matrix and $\mathcal{D}^*$ is its inverse in this band limited sense: $\mathcal{D}^* \mathcal{D}=\mathcal{I}$. Using these properties of the operators $\mathcal{I}$ and $\mathcal{D}$, one can verify that the real space operators satisfy the following identities,
%
\begin{subequations}
\beqry
\bar O_E  \bar O_E &=& \bar O_E;\qquad \bar O_B * \bar O_B = \bar O_B \,, \\
\bar O_E \bar O_B &=& 0 \,,\\
\bar O_E + \bar O_B &=& \mathcal{I} \,,
\eeqry
\end{subequations}
%
which are the real space analogues of \eq{eq:har_op_prop}.\footnote{While testing the above stated identities one encounters terms like $\mathcal{D} \mathcal{I}^*,\mathcal{I}^*\mathcal{I}$ and $\mathcal{I}\mathcal{I}^*$ which cannot be simply interpreted but they always occur in pairs with opposite signs that exactly cancel each other.}
